Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-29 manuscript/supplemental_material.Rnw
fix plot colors and a few more fixmes

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by \ac{FPKM} less
  than 1 were excluded from the plotted tree. Heatmap cells in grey
  are from species where there was no expression of the relevant
  transcript (or a species where that transcript does not apply).}

>>>>

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by FPKM less
  than 1 were excluded from the plotted tree. Heatmap cells in grey
  are from species where there was no expression of the relevant
  transcript (or a species where that transcript does not apply).}
